---
title: "hw5"
author: "Matthew Coulibaly Github: MattCoulibaly" 
date: "4/7/2020"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(readr)
library(tidyr)
library(dplyr)
library(ggplot2)
```

```{r}
#Question 1
sales = read_csv("2019_Iowa_Liquor_Sales2.csv")

#Question 2
tidysales = sales %>%
  separate('Date', c("Month", "Day", "Year"), sep = "/") %>%
  separate("Store Location", c("point", "Latitude", "Longitude"), sep = " ") %>%
  select(-point)
tidysales$Date = sales$Date
tidysales$Latitude = as.numeric(sub("\\(", "", tidysales$Latitude))
tidysales$Longitude = as.numeric(sub("\\)", "", tidysales$Longitude))

#Question 3
ggplot(tidysales, aes(x = Latitude, y = Longitude)) +
  geom_point() + xlim(-93.7, -93.57) + ylim(41.98, 42.07)

ggplot(tidysales, aes(x = tidysales$`Category Name`, y = tidysales$`Volume Sold (Gallons)`)) + xlab("Category Name") +
  ylab("Volume Sold (Gallons)") + geom_bar(stat = "identity")

#Question 4
daily = table(tidysales$Date)
summary(tidysales$`Bottles Sold`)
summary(tidysales$`Sale (Dollars)`)
summary(tidysales$`Volume Sold (Gallons)`)

#Question 5
tidysales$Month = factor(tidysales$Month, levels = c(1, 2, 3, 4, 5, 6, 7, 8, 9, 10, 11, 12))
ggplot(tidysales, aes(x = Date, y = tidysales$`Volume Sold (Gallons)`)) + geom_point() + facet_grid(.~tidysales$Month, scales = 'free') + geom_smooth() + ylab("Volume Sold (Galons)")
```

# Winter/spring months have more outliers than summer/fall months which seem to average a higher volume sold. Another pattern I noticed was that the lowest points in sales are during midterms(March/November), winter break(December/January), and summer(when students leave Ames).

# Question 6

# A pattern I noticed with the home football game dates in 2019 is that the volume sold skyrockets whenever there's a home game. For instance, 10/16/19 had the highest volume sold with more than 500 gallons and Iowa State had a home win on 10/12/19 and 10/19/19.
